MATH/COMP 562 ASSIGNMENT 3

### 2023-06-23 assignment-3/article.tex
Fix section headers
Tidy up exercise 3.5

%% \section*{Instructions}
%% Submit your solutions on MyCourses course page. You can get help from other students, but you should do the write up yourself. Code solutions can be a PDF of a workbook, you can use any programming language, but NumPy is recommended.

%% \section*{VC dimension}
%% Refer to “Foundations of Machine Learning,” by Mohri, Chapter 3.

\subsection*{Exercise 3.1 (Rademacher identities)}
\begin{problem}{Mohri Exercise 3.8. part (c) only}
Fix $m \geq 1$. Prove the following identity for any $\alpha \in \mathbb{R}$ and any two hypothesis sets $\mathcal{H}$ and $\mathcal{H}_0$ of functions mapping from $\mathcal{X}$ to $\mathbb{R}$:

@@

@@

\section*{Stability Theory}

Exercise 3.5 (Strong Convexity). Recall that a function $f$ is $\lambda$-strongly convex if
\[
\alpha f(w) + (1 - \alpha)f(u) \geq f(\alpha w + (1 - \alpha)u) + \frac{\lambda}{2} \alpha(1 - \alpha)\|w - u\|^2, \quad \forall u, w \in \mathbb{R}^d , \alpha \in [0, 1]
\]

\begin{enumerate}
    \item Prove that $f(w) = \|w\|^2$ is $\lambda$-strongly convex with $\lambda = 2$.

    \item Give an example of a convex function which is not $\lambda$-strongly convex for any $\lambda > 0$.

    \item Let $f : \mathbb{R}^d \rightarrow \mathbb{R}$ be convex. Prove that $g(w, \lambda) = f(w) + \frac{\lambda}{2}\|w\|^2$ is $\lambda$-strongly convex.

    \item Prove that $g$ is $\lambda$-strongly convex if and only if $f(w) = g(w) - \frac{\lambda}{2}\|w\|^2$ is convex.

% Continuing from the previous LaTeX document

\section*{Continuation of Exercises}

>>>>

\section*{Rademacher Complexity}
\subsection*{Exercise 3.1 (Rademacher identities)}
\begin{problem}{Mohri Exercise 3.8. part (c) only}
Fix $m \geq 1$. Prove the following identity for any $\alpha \in \mathbb{R}$ and any two hypothesis sets $\mathcal{H}$ and $\mathcal{H}_0$ of functions mapping from $\mathcal{X}$ to $\mathbb{R}$:

@@

\section{VC dimension}

@@

\section*{Stability Theory}
Recall that a function $f$ is $\lambda$-strongly convex if for all $u, w \in \mathbb{R}^d , \alpha \in [0, 1]$:
$$f(\alpha w + (1 - \alpha)u) + \frac{\lambda}{2} \alpha(1 - \alpha)\|w - u\|^2 \leq \alpha f(w) + (1 - \alpha)f(u)$$
\begin{problem}{Exercise 3.5 (Strong convexity)}
  \begin{enumerate}[label=(\alph*)]
    \item Prove that $f(w) = \|w\|^2$ is $\lambda$-strongly convex with $\lambda = 2$.
    \item Give an example of a convex function which is not $\lambda$-strongly convex for any $\lambda > 0$.
    \item Let $f : \mathbb{R}^d \rightarrow \mathbb{R}$ be convex. Prove that $g(w, \lambda) = f(w) + \frac{\lambda}{2}\|w\|^2$ is $\lambda$-strongly convex.
    \item Prove that $g$ is $\lambda$-strongly convex if and only if $f(w) = g(w) - \frac{\lambda}{2}\|w\|^2$ is convex.
  \end{enumerate}
\end{problem}
